### 2020-01-15 draft.tex
Updating .gitignore to remove LaTeX garbage and .R output like files and tables
Updating master.sh to properly compile bibtex
Changed some 1st person single wording in the abstract to 1st person plural

\date{May 28, 2019}

@@

The Renewable Fuel Standard (RFS), which requires oil refineries to blend ethanol into domestic fuel supplies, is a market-based policy that implements tradable compliance credits (called RINs) to better equalize compliance costs across firms. I use variation in the prices of these credits to retrieve reduced-form estimates of how the RFS impacts the stock prices of refining firms. I take advantage of unanticipated regulatory announcements that caused major swings in RIN prices to implement an event study around those announcement dates and also fit bivariate time series models to firm $\times$ RIN pairs. Both models show no significant stock price response among small or medium size firms and a small but statistically significant price response among large refiners. These findings are relevant to policy in that they cast doubt on concerns that the RFS allows integrated refiners to abuse merchant refiners. Our findings also shed light on the necessity of Small Refinery Exemptions, which are intended to shield small, financially vulnerable refiners from RFS compliance costs.
\newline

>>>>

\date{January 14, 2020}

@@

The Renewable Fuel Standard (RFS), which requires oil refineries to blend ethanol into domestic fuel supplies, is a market-based policy that implements tradable compliance credits (called RINs) to better equalize compliance costs across firms. We use variation in the prices of these credits to retrieve reduced-form estimates of how the RFS impacts the stock prices of refining firms. We take advantage of unanticipated regulatory announcements that caused major swings in RIN prices to implement an event study around those announcement dates and also fit bivariate time series models to firm $\times$ RIN pairs. Both models show no significant stock price response among small or medium size firms and a small but statistically significant price response among large refiners. These findings are relevant to policy in that they cast doubt on concerns that the RFS allows integrated refiners to abuse merchant refiners. Our findings also shed light on the necessity of Small Refinery Exemptions, which are intended to shield small, financially vulnerable refiners from RFS compliance costs.
\newline
